Notes from the President

### 2013-09-19 pnsac/newsletter/article_PresReport.tex
Changed directory name. Primary newsletter files now in newsletter/

@@

With the initiatives above, we are hoping in the next few months to
consolidate our position as an important organization working with the
Aviation Museum

>>>>

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   %name of the graphic, without the path AND in EPS format:
   \includegraphics[scale=0.5]{canadaday_visitor.eps}
   %caption of the figure 
   \caption*{\small \em Showing off the North Star on Canada Day -- an
   impressed visitor examines the cockpit.}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:canadaday}
\end{figure}

@@

With the initiatives above, we are hoping in the next few months to
consolidate our position as an important organization working with the
Aviation Museum.
